---
title: "McDonaldsSentimentAnalysis"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

######################################################
#Code for Installing and Loading the Required packages
#####################################################

```{r}

InstallAndLoadPackages<-function(x) 
{  
x <- as.character(x)  
if (!require(x,character.only=TRUE))  
       {
   		 install.packages(pkgs=x,repos="http://cran.r-project.org") 
   		 require(x,character.only=TRUE)  
       }	 	
}

PrepareTwitter<-function() {  
InstallAndLoadPackages("bitops") 
InstallAndLoadPackages("RCurl")  
InstallAndLoadPackages("RJSONIO")  
InstallAndLoadPackages("ROAuth")
InstallAndLoadPackages("SnowballC")
InstallAndLoadPackages("modeest")
InstallAndLoadPackages("tm")
InstallAndLoadPackages("rJava")
InstallAndLoadPackages("RWeka")
InstallAndLoadPackages("RWekajars")
InstallAndLoadPackages("stopwords")

InstallAndLoadPackages("twitteR")  
InstallAndLoadPackages("wordcloud")
InstallAndLoadPackages("tidytext")
InstallAndLoadPackages("topicmodels")

}

PrepareTwitter()
```
######################################################
#Get the following info from yout Twitter account. Fill in your consumer key, consumer secret, access token and accesstoken secret here

Create four variables and call them:
* consumer_key
* consumer_secret
* access_token
* access_token_secret

And then run the following command:
setup_twitter_oauth(consumer_key, consumer_secret, access_token, access_token_secret)

########################################################
```{r, echo=FALSE}
consumer_key=""
consumer_secret=""
access_token=""
access_token_secret=""
##To set up Twitter Authorization during R session. To gain access to Twitter
setup_twitter_oauth(consumer_key, consumer_secret, access_token, access_token_secret)

##mode(tweetlist)
##str(head(tweetList,1))
##length(tweetList)

```
#Define function to get tweets based on a search term - e.g. Brand. Return n tweets SINCE year as a dataframe
``` {r}
TweetFrame<-function(searchTerm,n,SINCE) 
	{  
		# This function TweetFrame() - Return a dataframe based on a search of Twitter 
		tweetList <- searchTwitter(searchTerm,n,since=SINCE,lang='en')    

		# as.data.frame() coerces each list element into a row  
		# lapply() applies this to all of the elements in twtList  
		# rbind() takes all of the rows and puts them together  
		# do.call() gives rbind() all rows as individual elements  

		tweetDF<- do.call("rbind", lapply(tweetList,as.data.frame))    
		# This last step sorts the tweets in arrival order  

		return(tweetDF[order(as.integer(tweetDF$created)), ]) 
	}
```
#Get tweets for keywords mcdonalds, wendys, burgerking, arbys, kfc, and subway and store them in separate dataframes
```{r}

mcdonalds0203=TweetFrame("#mcdonalds",5000,'2022-12-01')
wendys0203=TweetFrame("#wendys",5000,'2022-12-01')
burgerking0203=TweetFrame("#burgerking",5000,'2022-12-01')
arbys0203=TweetFrame("#arbys",5000,'2022-12-01')
kfc0203=TweetFrame("#kfc",5000,'2022-12-01')
subway0203=TweetFrame("#subway",5000,'2022-12-01')

##Combine all dataframes into one larger cell dataframe
cell=rbind(mcdonalds0203,subway0203,kfc0203)

hist(cell$created,breaks=15,freq=TRUE)
mfv(as.integer(diff(cell$created))) 

```
```{r}
mcdonalds0303=TweetFrame("#mcdonalds",5000,'2022-12-01')
wendys0303=TweetFrame("#wendys",5000,'2022-12-01')
burgerking0303=TweetFrame("#burgerking",5000,'2022-12-01')
arbys0303=TweetFrame("#arbys",5000,'2022-12-01')
kfc0303=TweetFrame("#kfc",5000,'2022-12-01')
subway0303=TweetFrame("#subway",5000,'2022-12-01')
```
```{r}
mcdonalds0403=TweetFrame("#mcdonalds",5000,'2022-12-01')
wendys0403=TweetFrame("#wendys",5000,'2022-12-01')
burgerking0403=TweetFrame("#burgerking",5000,'2022-12-01')
arbys0403=TweetFrame("#arbys",5000,'2022-12-01')
kfc0403=TweetFrame("#kfc",5000,'2022-12-01')
subway0403=TweetFrame("#subway",5000,'2022-12-01')
```
```{r}
chipotle0403=TweetFrame("#chipotle",5000,'2022-12-01')
chickfila0403=TweetFrame("#chickfila",5000,'2022-12-01')
```
```{r}
starbucks0403 = TweetFrame("#starbucks",5000,'2022-12-01')
```
```{r}
tacobell0403=TweetFrame("#tacobell",5000,'2022-12-01')
dunkin0403=TweetFrame("#dunkin",5000,'2022-12-01')
dominos0403=TweetFrame("#dominos",5000,'2022-12-01')
```

```{r}
starbucksfull = starbucks0403
mcdonaldsfull = merge(mcdonaldsfull, mcdonalds0403, all = TRUE)
subwayfull = merge(subwayfull, subway0403, all = TRUE)
kfcfull = merge(kfcfull, kfc0403, all = TRUE)

##Combine all dataframes into one larger cell dataframe
cell=rbind(mcdonaldsfull,subwayfull,kfcfull, starbucksfull)

hist(cell$created,breaks=15,freq=TRUE)
mfv(as.integer(diff(cell$created))) 
```
```{r}
mcdonalds0503=TweetFrame("#mcdonalds",5000,'2022-12-01')
kfc0503=TweetFrame("#kfc",5000,'2022-12-01')
subway0503=TweetFrame("#subway",5000,'2022-12-01')
starbucks0503 = TweetFrame("#starbucks",5000,'2022-12-01')
```

```{r}
mcdonalds0603=TweetFrame("#mcdonalds",5000,'2022-12-01')
kfc0603=TweetFrame("#kfc",5000,'2022-12-01')
subway0603=TweetFrame("#subway",5000,'2022-12-01')
starbucks0603 = TweetFrame("#starbucks",5000,'2022-12-01')
```
```{r}
mcdonaldsfull.unique <- mcdonaldsfull %>%
  group_by(id) %>%
  summarise(text = first(text), created = first(created))

starbucksfull.unique <- starbucksfull %>%
  group_by(id) %>%
  summarise(text = first(text), created = first(created))

subwayfull.unique <- subwayfull %>%
  group_by(id) %>%
  summarise(text = first(text), created = first(created))

kfcfull.unique <- kfcfull %>%
  group_by(id) %>%
  summarise(text = first(text), created = first(created))
```


```{r}
starbucksfull = merge(starbucksfull, starbucks0603, all = TRUE)
mcdonaldsfull = merge(mcdonaldsfull, mcdonalds0603, all = TRUE)
subwayfull = merge(subwayfull, subway0603, all = TRUE)
kfcfull = merge(kfcfull, kfc0603, all = TRUE)

##Combine all dataframes into one larger cell dataframe
cell=rbind(mcdonaldsfull,subwayfull,kfcfull, starbucksfull)

# group the data frame by the "id" column and keep the first value of all other columns
cell <- cell %>%
  group_by(id) %>%
  summarise(text = first(text), created = first(created))

hist(cell$created,breaks=15,freq=TRUE)
mfv(as.integer(diff(cell$created))) 
```

#Converting Dataframe to a Corpus from Tweeted text vectors and cleaning text
```{r}
myStopwords = c(stopwords(source = "snowball"),
                stopwords(source = "stopwords-iso"),
                stopwords(source = "smart"),
              "...", "’s", "🀭", "❤️", "👲", "🔯", "⭐️", "ownerwillcarry", "drawluca…")
myStopwords = unique(myStopwords)

Corpus.cell = Corpus(VectorSource(cell$text))
myCorpus=Corpus.cell

# remove stopwords
# I HAVE ALREADY DEFINED MY STOPWORDS IN MyStopwords
myStopwords <- stopwords('english')
myCorpus2 <- tm_map(myCorpus, removeWords, myStopwords)
# remove punctuation
myCorpus2 <- tm_map(myCorpus2, removePunctuation)
# remove numbers
myCorpus2 <- tm_map(myCorpus2, removeNumbers)
# Convert all Alphabets to lowercase
myCorpus2 <- tm_map(myCorpus2, tolower)
```
####Construct a Term x Document matrix
```{r}
TDM_cell <- TermDocumentMatrix(myCorpus2, control = list(minWordLength = 5))
dim(TDM_cell)
inspect(TDM_cell[1:20,20:30])
head(TDM_cell)
```
##### Produce a WordCloud
#calculate the frequency of words
```{r}
freeq <- sort(rowSums(as.matrix(TDM_cell)), decreasing=TRUE)
myNames <- names(freeq)
d <- data.frame(word=names(freeq), freq=freeq)
wordcloud(d$word, d$freq, min.freq=50)
```
###############################
### K-means clustering on TDM 
#################################
## Documents will be clustered based on topics discussed
### Analogous to Topic Modeling
#########################################

```{r}
cell.kmeans.3 <- kmeans(t(TDM_cell), centers = 3, nstart=5)
sort(cell.kmeans.3$centers[1,],decreasing=TRUE)[1:100]
table(cell.kmeans.3$cluster)
```

############################
#======TOPIC MODELING IN R using package topicmodels.
## Using function LDA - Latent Dirichlet Allocation modeling approach.
############################

```{r}
set.seed(123)
system.time(cell.topicmodel5 <- topicmodels::LDA(t(TDM_cell), 5, method = "Gibbs", control = list(iter=2000, seed = 0622)))
cell.topics5 <- topicmodels::topics(cell.topicmodel5, 1)
## In this case I am returning the top 30 terms.
cell.terms.5topics <- as.data.frame(topicmodels::terms(cell.topicmodel5, 50), stringsAsFactors = FALSE)
##Viewing the topics
head(cell.terms.5topics)
```
```{r}
# Compute coherence scores for the topics in your model
topic_diagnostics(cell.topicmodel5, t(TDM_cell))
```
```{r}
topic_size(cell.topicmodel5)
mean_token_length(cell.topicmodel5)
```

```{r}
set.seed(123)
system.time(cell.topicmodel10 <- topicmodels::LDA(t(TDM_cell), 10, method = "Gibbs", control = list(iter=2000, seed = 0622)))
cell.topics10 <- topicmodels::topics(cell.topicmodel10, 1)
## In this case I am returning the top 10 terms.
cell.terms.10topics <- as.data.frame(topicmodels::terms(cell.topicmodel10, 50), stringsAsFactors = FALSE)
##Viewing the topics
head(cell.terms.10topics)
```
```{r}
library("text2vec")
library("topicdoc")
```
```{r}
# Compute coherence scores for the topics in your model
topic_diagnostics(cell.topicmodel10, t(TDM_cell))
```
```{r}
topic_size(cell.topicmodel10)
mean_token_length(cell.topicmodel)
```
# For 10 topic:
# 4: Brand reputation
# 6: Advertising and Promotions
# 7: Food and Beverages
# 10: Social Media Engagement

```{r}
set.seed(123)
system.time(cell.topicmodel15 <- topicmodels::LDA(t(TDM_cell), 15, method = "Gibbs", control = list(iter=2000, seed = 0622)))
cell.topics15 <- topicmodels::topics(cell.topicmodel15, 1)
## In this case I am returning the top 30 terms.
cell.terms.15topics <- as.data.frame(topicmodels::terms(cell.topicmodel15, 50), stringsAsFactors = FALSE)
##Viewing the topics
head(cell.terms.15topics)
```
```{r}
# Compute coherence scores for the topics in your model
topic_diagnostics(cell.topicmodel15, t(TDM_cell))
```
```{r}
topic_size(cell.topicmodel15)
mean_token_length(cell.topicmodel15)
```
# For 15 topic:
# 4: Food and Beverages
# 6: Brand reputation
# 8: Advertising and Promotions
# 10: Mcdonalds
# 14: Social Media Engagement
# 15: Beverages


# We use LDA with 10 topics and use:
# 4: Brand reputation
# 6: Advertising and Promotions
# 7: Food and Beverages
# 10: Social Media Engagement

# Most frequent words in all tweets:
```{r}
# Plot a horizontal histogram
library(ggplot2)

ggplot(head(d,30), aes(x = (reorder(word, freq)), y = freq)) +
    geom_col() +
    labs(title="All Brand Tweets",
         x = "Words",
         y = "Frequency") +
    coord_flip()
```
#Topic 4 word frequencies: Brand Reputation
```{r}
search_pattern <- str_c(cell.terms.10topics$`Topic 4`, collapse = "|")
matches <- str_extract_all(cell$text, search_pattern)
contains_word <- lengths(matches) > 0
sentences_with_word <- cell[contains_word, ]

# Cleaning tweets
myStopwords = c(stopwords(source = "snowball"),
                stopwords(source = "stopwords-iso"),
                stopwords(source = "smart"))
myStopwords = unique(myStopwords)
Corpus.cell_topic4 = Corpus(VectorSource(sentences_with_word$text))
myCorpus_topic4=Corpus.cell_topic4
##### remove stopwords
### I HAVE ALREADY DEFINED MY STOPWORDS IN MyStopwords
myStopwords <- stopwords('english')
myCorpus_topic4 <- tm_map(myCorpus_topic4, removeWords, myStopwords)
# remove punctuation
myCorpus_topic4 <- tm_map(myCorpus_topic4, removePunctuation)
# remove numbers
myCorpus_topic4 <- tm_map(myCorpus_topic4, removeNumbers)
# Convert all Alphabets to lowercase
#myCorpus2 <- tm_map(myCorpus2, tolower)

####Construct a Term x Document matrix
TDM_cell_topic4 <- TermDocumentMatrix(myCorpus_topic4, control = list(minWordLength = 5))
dim(TDM_cell_topic4)
inspect(TDM_cell_topic4[1:20,20:30])
head(TDM_cell_topic4)

##### Produce a WordCloud
#calculate the frequency of words
freeq_topic4 <- sort(rowSums(as.matrix(TDM_cell_topic4)), decreasing=TRUE)
myNames_topic4 <- names(freeq_topic4)
d_topic4 <- data.frame(word=names(freeq_topic4), freq=freeq_topic4)
wordcloud(d_topic4$word, d_topic4$freq, min.freq=50)
```

```{r}
# Plot a horizontal histogram with 2 columns
ggplot(head(d_topic4,30), aes(x = (reorder(word, freq)), y = freq)) +
    geom_col() +
    labs(title="Topic 4 Tweets",
         x = "Words",
         y = "Frequency") +
    coord_flip()
```
```{r}
topic4_hist = merge(d, d_topic4, by = "word", all = FALSE)
topic4_hist = topic4_hist[order(topic4_hist$freq.y, decreasing = TRUE),]
topic4_hist
```
```{r}
# Plot a horizontal histogram with 2 columns
ggplot(head(topic4_hist,30), aes(x = reorder(word, freq.y))) +
  geom_col(aes(y = freq.y, fill = "Frequency in topic 4"), alpha = 1) +
  geom_col(aes(y = freq.x, fill = "Overall Frequency"), alpha = 0.5) +
  scale_fill_manual(values = c("cyan", "darkgoldenrod1"))+
  labs(title="Topic 4 Tweets Word Fequency",
        x = "Words",
        y = "Frequency") +
  guides(fill = guide_legend(title = "Y-axis")) +
  coord_flip()
```
```{r}
search_pattern <- paste("\\b(", paste(cell.terms.10topics$`Topic 4`[1:15], collapse = "|"), ")\\b", sep = "")
matches <- str_extract_all(topic4_hist$word, search_pattern)
is_word <- lengths(matches) > 0
words_found <- topic4_hist[is_word, ]

# Plot a horizontal histogram with words in top 10 of topic 1
ggplot(head(words_found,10), aes(x = reorder(word, freq.y))) +
  geom_col(aes(y = freq.y, fill = "Frequency in topic 4"), alpha = 1) +
  geom_col(aes(y = freq.x, fill = "Overall Frequency"), alpha = 0.5) +
  scale_fill_manual(values = c("cyan", "darkgoldenrod1"))+
  labs(title="Topic 4 Key Words Frequency",
        x = "Words",
        y = "Frequency") +
  guides(fill = guide_legend(title = "Y-axis")) +
  coord_flip()
```
#Topic 6 word frequencies: Advertising and Promotions
```{r}
search_pattern <- str_c(cell.terms.10topics$`Topic 6`, collapse = "|")
matches <- str_extract_all(cell$text, search_pattern)
contains_word <- lengths(matches) > 0
sentences_with_word <- cell[contains_word, ]

# Cleaning tweets
myStopwords = c(stopwords(source = "snowball"),
                stopwords(source = "stopwords-iso"),
                stopwords(source = "smart"))
myStopwords = unique(myStopwords)
Corpus.cell_topic6 = Corpus(VectorSource(sentences_with_word$text))
myCorpus_topic6=Corpus.cell_topic6
##### remove stopwords
### I HAVE ALREADY DEFINED MY STOPWORDS IN MyStopwords
myStopwords <- stopwords('english')
myCorpus_topic6 <- tm_map(myCorpus_topic6, removeWords, myStopwords)
# remove punctuation
myCorpus_topic6 <- tm_map(myCorpus_topic6, removePunctuation)
# remove numbers
myCorpus_topic6 <- tm_map(myCorpus_topic6, removeNumbers)
# Convert all Alphabets to lowercase
#myCorpus2 <- tm_map(myCorpus2, tolower)

####Construct a Term x Document matrix
TDM_cell_topic6 <- TermDocumentMatrix(myCorpus_topic6, control = list(minWordLength = 5))
dim(TDM_cell_topic6)
inspect(TDM_cell_topic6[1:20,20:30])
head(TDM_cell_topic6)

##### Produce a WordCloud
#calculate the frequency of words
freeq_topic6 <- sort(rowSums(as.matrix(TDM_cell_topic6)), decreasing=TRUE)
myNames_topic6 <- names(freeq_topic6)
d_topic6 <- data.frame(word=names(freeq_topic6), freq=freeq_topic6)
wordcloud(d_topic6$word, d_topic6$freq, min.freq=50)
```
```{r}
# Plot a horizontal histogram with 2 columns
ggplot(head(d_topic6,30), aes(x = (reorder(word, freq)), y = freq)) +
    geom_col() +
    labs(title="Topic 6 Tweets",
         x = "Words",
         y = "Frequency") +
    coord_flip()
```
```{r}
topic6_hist = merge(d, d_topic6, by = "word", all = FALSE)
topic6_hist = topic6_hist[order(topic6_hist$freq.y, decreasing = TRUE),]
# Plot a horizontal histogram with 2 columns
ggplot(head(topic6_hist,30), aes(x = reorder(word, freq.y))) +
  geom_col(aes(y = freq.y, fill = "Frequency in topic 6"), alpha = 1) +
  geom_col(aes(y = freq.x, fill = "Overall Frequency"), alpha = 0.5) +
  scale_fill_manual(values = c("cyan", "darkgoldenrod1"))+
  labs(title="Topic 6 Tweets Word Fequency",
        x = "Words",
        y = "Frequency") +
  guides(fill = guide_legend(title = "Y-axis")) +
  coord_flip()
```
```{r}
search_pattern <- paste("\\b(", paste(cell.terms.10topics$`Topic 6`[1:15], collapse = "|"), ")\\b", sep = "")
matches <- str_extract_all(topic6_hist$word, search_pattern)
is_word <- lengths(matches) > 0
words_found <- topic6_hist[is_word, ]

# Plot a horizontal histogram with words in top 10 of topic 1
ggplot(head(words_found,10), aes(x = reorder(word, freq.y))) +
  geom_col(aes(y = freq.y, fill = "Frequency in topic 6"), alpha = 1) +
  geom_col(aes(y = freq.x, fill = "Overall Frequency"), alpha = 0.5) +
  scale_fill_manual(values = c("cyan", "darkgoldenrod1"))+
  labs(title="Topic 6 Key Words Frequency",
        x = "Words",
        y = "Frequency") +
  guides(fill = guide_legend(title = "Y-axis")) +
  coord_flip()
```

#Topic 7 word frequencies: Food and Beverages
```{r}
search_pattern <- str_c(cell.terms.10topics$`Topic 7`, collapse = "|")
matches <- str_extract_all(cell$text, search_pattern)
contains_word <- lengths(matches) > 0
sentences_with_word <- cell[contains_word, ]

# Cleaning tweets
myStopwords = c(stopwords(source = "snowball"),
                stopwords(source = "stopwords-iso"),
                stopwords(source = "smart"))
myStopwords = unique(myStopwords)
Corpus.cell_topic7 = Corpus(VectorSource(sentences_with_word$text))
myCorpus_topic7=Corpus.cell_topic7
##### remove stopwords
### I HAVE ALREADY DEFINED MY STOPWORDS IN MyStopwords
myStopwords <- stopwords('english')
myCorpus_topic7 <- tm_map(myCorpus_topic7, removeWords, myStopwords)
# remove punctuation
myCorpus_topic7 <- tm_map(myCorpus_topic7, removePunctuation)
# remove numbers
myCorpus_topic7 <- tm_map(myCorpus_topic7, removeNumbers)
# Convert all Alphabets to lowercase
#myCorpus2 <- tm_map(myCorpus2, tolower)

####Construct a Term x Document matrix
TDM_cell_topic7 <- TermDocumentMatrix(myCorpus_topic7, control = list(minWordLength = 5))
dim(TDM_cell_topic7)
inspect(TDM_cell_topic7[1:20,20:30])
head(TDM_cell_topic7)

##### Produce a WordCloud
#calculate the frequency of words
freeq_topic7 <- sort(rowSums(as.matrix(TDM_cell_topic7)), decreasing=TRUE)
myNames_topic7 <- names(freeq_topic7)
d_topic7 <- data.frame(word=names(freeq_topic7), freq=freeq_topic7)
wordcloud(d_topic7$word, d_topic7$freq, min.freq=50)
```

```{r}
# Plot a horizontal histogram with 2 columns
ggplot(head(d_topic7,30), aes(x = (reorder(word, freq)), y = freq)) +
    geom_col() +
    labs(title="Topic 7 Tweets",
         x = "Words",
         y = "Frequency") +
    coord_flip()
```
```{r}
topic7_hist = merge(d, d_topic7, by = "word", all = FALSE)
topic7_hist = topic7_hist[order(topic7_hist$freq.y, decreasing = TRUE),]
topic7_hist
```
```{r}
# Plot a horizontal histogram with 2 columns
ggplot(head(topic7_hist,10), aes(x = reorder(word, freq.y))) +
  geom_col(aes(y = freq.y, fill = "Frequency in topic 7"), alpha = 1) +
  geom_col(aes(y = freq.x, fill = "Overall Frequency"), alpha = 0.5) +
  scale_fill_manual(values = c("cyan", "darkgoldenrod1"))+
  labs(title="Topic 7 Tweets Word Fequency",
        x = "Words",
        y = "Frequency") +
  guides(fill = guide_legend(title = "Y-axis")) +
  coord_flip()
```
```{r}
search_pattern <- paste("\\b(", paste(cell.terms.10topics$`Topic 7`[1:15], collapse = "|"), ")\\b", sep = "")
matches <- str_extract_all(topic7_hist$word, search_pattern)
is_word <- lengths(matches) > 0
words_found <- topic7_hist[is_word, ]

# Plot a horizontal histogram with words in top 10 of topic 1
ggplot(head(words_found,10), aes(x = reorder(word, freq.y))) +
  geom_col(aes(y = freq.y, fill = "Frequency in topic 7"), alpha = 1) +
  geom_col(aes(y = freq.x, fill = "Overall Frequency"), alpha = 0.5) +
  scale_fill_manual(values = c("cyan", "darkgoldenrod1"))+
  labs(title="Topic 7 Key Words Frequency",
        x = "Words",
        y = "Frequency") +
  guides(fill = guide_legend(title = "Y-axis")) +
  coord_flip()
```
# Topic 10 Word Frequency: Social Media Engagement
```{r}
search_pattern <- str_c(cell.terms.10topics$`Topic 10`, collapse = "|")
matches <- str_extract_all(cell$text, search_pattern)
contains_word <- lengths(matches) > 0
sentences_with_word <- cell[contains_word, ]

# Cleaning tweets
myStopwords = c(stopwords(source = "snowball"),
                stopwords(source = "stopwords-iso"),
                stopwords(source = "smart"))
myStopwords = unique(myStopwords)
Corpus.cell_topic10 = Corpus(VectorSource(sentences_with_word$text))
myCorpus_topic10=Corpus.cell_topic10
##### remove stopwords
### I HAVE ALREADY DEFINED MY STOPWORDS IN MyStopwords
myStopwords <- stopwords('english')
myCorpus_topic10 <- tm_map(myCorpus_topic10, removeWords, myStopwords)
# remove punctuation
myCorpus_topic10 <- tm_map(myCorpus_topic10, removePunctuation)
# remove numbers
myCorpus_topic10 <- tm_map(myCorpus_topic10, removeNumbers)
# Convert all Alphabets to lowercase
#myCorpus2 <- tm_map(myCorpus2, tolower)

####Construct a Term x Document matrix
TDM_cell_topic10 <- TermDocumentMatrix(myCorpus_topic10, control = list(minWordLength = 5))
dim(TDM_cell_topic10)
inspect(TDM_cell_topic10[1:20,20:30])
head(TDM_cell_topic10)

##### Produce a WordCloud
#calculate the frequency of words
freeq_topic10 <- sort(rowSums(as.matrix(TDM_cell_topic10)), decreasing=TRUE)
myNames_topic7 <- names(freeq_topic10)
d_topic10 <- data.frame(word=names(freeq_topic10), freq=freeq_topic10)
wordcloud(d_topic10$word, d_topic10$freq, min.freq=50)
```

```{r}
# Plot a horizontal histogram with 2 columns
ggplot(head(d_topic10,30), aes(x = (reorder(word, freq)), y = freq)) +
    geom_col() +
    labs(title="Topic 10 Tweets",
         x = "Words",
         y = "Frequency") +
    coord_flip()
```
```{r}
topic10_hist = merge(d, d_topic10, by = "word", all = FALSE)
topic10_hist = topic10_hist[order(topic10_hist$freq.y, decreasing = TRUE),]
topic10_hist
```
```{r}
# Plot a horizontal histogram with 2 columns
ggplot(head(topic10_hist,10), aes(x = reorder(word, freq.y))) +
  geom_col(aes(y = freq.y, fill = "Frequency in topic 10"), alpha = 1) +
  geom_col(aes(y = freq.x, fill = "Overall Frequency"), alpha = 0.5) +
  scale_fill_manual(values = c("cyan", "darkgoldenrod1"))+
  labs(title="Topic 10 Tweets Word Fequency",
        x = "Words",
        y = "Frequency") +
  guides(fill = guide_legend(title = "Y-axis")) +
  coord_flip()
```
```{r}
search_pattern <- paste("\\b(", paste(cell.terms.10topics$`Topic 10`[1:15], collapse = "|"), ")\\b", sep = "")
matches <- str_extract_all(topic10_hist$word, search_pattern)
is_word <- lengths(matches) > 0
words_found <- topic10_hist[is_word, ]

# Plot a horizontal histogram with words in top 10 of topic 1
ggplot(head(words_found,10), aes(x = reorder(word, freq.y))) +
  geom_col(aes(y = freq.y, fill = "Frequency in topic 10"), alpha = 1) +
  geom_col(aes(y = freq.x, fill = "Overall Frequency"), alpha = 0.5) +
  scale_fill_manual(values = c("cyan", "darkgoldenrod1"))+
  labs(title="Topic 10 Key Words Frequency",
        x = "Words",
        y = "Frequency") +
  guides(fill = guide_legend(title = "Y-axis")) +
  coord_flip()
```

# Sentiment Analysis:
```{r}
library(rtweet)
library(tidytext)
library("textdata")
```

#FOR TOPIC 4: Brand reputation
```{r}
search_pattern <- paste("\\b(", paste(cell.terms.10topics$`Topic 4`[1:15], collapse = "|"), ")\\b", sep = "")
matches <- str_extract_all(cell$text, search_pattern)
contains_word <- lengths(matches) > 0
sentences_with_word <- cell[contains_word, ]

tidy_tweets <- sentences_with_word %>%
  unnest_tokens(word, text)
```
```{r}
sentiments <- get_sentiments("afinn")
tweet_sentiments <- tidy_tweets %>%
  inner_join(sentiments) %>%
  group_by(id) %>%
  summarize(sentiment_score = sum(value)) %>%
  ungroup()
```
```{r}
library(ggplot2)
ggplot(tweet_sentiments, aes(x = sentiment_score)) +
  geom_histogram() +
  labs(title = "Sentiment of All tweets for Topic 4",
       x = "Sentiment score", y = "Count")
```
```{r}
mean(tweet_sentiments$sentiment_score)
```
```{r}
mean(merge(tweet_sentiments, mcdonaldsfull, by = "id", all = FALSE)$sentiment_score)
```
```{r}
mean(merge(tweet_sentiments, kfcfull, by = "id", all = FALSE)$sentiment_score)
```

```{r}
mean(merge(tweet_sentiments, subwayfull , by = "id", all = FALSE)$sentiment_score)
```
```{r}
mean(merge(tweet_sentiments, starbucksfull , by = "id", all = FALSE)$sentiment_score)
```

# FOR TOPIC 6: Sales and Promotions
```{r}
search_pattern <- str_c(cell.terms.10topics$`Topic 6`[1:10], collapse = "|")
matches <- str_extract_all(cell$text, search_pattern)
contains_word <- lengths(matches) > 0
sentences_with_word <- cell[contains_word, ]

tidy_tweets <- sentences_with_word %>%
  unnest_tokens(word, text)
```

```{r}
sentiments <- get_sentiments("afinn")
tweet_sentiments <- tidy_tweets %>%
  inner_join(sentiments) %>%
  group_by(id) %>%
  summarize(sentiment_score = sum(value)) %>%
  ungroup()
```
```{r}
library(ggplot2)
ggplot(tweet_sentiments, aes(x = sentiment_score)) +
  geom_histogram() +
  labs(title = "Sentiment of All tweets for Topic 6:",
       x = "Sentiment score", y = "Count")
```
```{r}
mean(tweet_sentiments$sentiment_score)
```
```{r}
mean(merge(tweet_sentiments, mcdonaldsfull, by = "id", all = FALSE)$sentiment_score)
```
```{r}
mean(merge(tweet_sentiments, kfcfull, by = "id", all = FALSE)$sentiment_score)
```

```{r}
mean(merge(tweet_sentiments, subwayfull, by = "id", all = FALSE)$sentiment_score)
```
```{r}
mean(merge(tweet_sentiments, starbucksfull , by = "id", all = FALSE)$sentiment_score)
```

#FOR TOPIC 7: Food and Beverages
```{r}
search_pattern <- paste("\\b(", paste(cell.terms.10topics$`Topic 7`[1:15], collapse = "|"), ")\\b", sep = "")
matches <- str_extract_all(cell$text, search_pattern)
contains_word <- lengths(matches) > 0
sentences_with_word <- cell[contains_word, ]

tidy_tweets <- sentences_with_word %>%
  unnest_tokens(word, text)
```
```{r}
sentiments <- get_sentiments("afinn")
tweet_sentiments <- tidy_tweets %>%
  inner_join(sentiments) %>%
  group_by(id) %>%
  summarize(sentiment_score = sum(value)) %>%
  ungroup()
```
```{r}
library(ggplot2)
ggplot(tweet_sentiments, aes(x = sentiment_score)) +
  geom_histogram() +
  labs(title = "Sentiment of All tweets for Topic 7",
       x = "Sentiment score", y = "Count")
```
```{r}
mean(tweet_sentiments$sentiment_score)
```
```{r}
mean(merge(tweet_sentiments, mcdonaldsfull, by = "id", all = FALSE)$sentiment_score)
```
```{r}
mean(merge(tweet_sentiments, kfcfull, by = "id", all = FALSE)$sentiment_score)
```

```{r}
mean(merge(tweet_sentiments, subwayfull , by = "id", all = FALSE)$sentiment_score)
```
```{r}
mean(merge(tweet_sentiments, starbucksfull , by = "id", all = FALSE)$sentiment_score)
```

#FOR TOPIC 10: Social Media Engagement
```{r}
search_pattern <- paste("\\b(", paste(cell.terms.10topics$`Topic 10`[1:15], collapse = "|"), ")\\b", sep = "")
matches <- str_extract_all(cell$text, search_pattern)
contains_word <- lengths(matches) > 0
sentences_with_word <- cell[contains_word, ]

tidy_tweets <- sentences_with_word %>%
  unnest_tokens(word, text)
```
```{r}
sentiments <- get_sentiments("afinn")
tweet_sentiments <- tidy_tweets %>%
  inner_join(sentiments) %>%
  group_by(id) %>%
  summarize(sentiment_score = sum(value)) %>%
  ungroup()
```
```{r}
library(ggplot2)
ggplot(tweet_sentiments, aes(x = sentiment_score)) +
  geom_histogram() +
  labs(title = "Sentiment of All tweets for Topic 10",
       x = "Sentiment score", y = "Count")
```
```{r}
mean(tweet_sentiments$sentiment_score)
```
```{r}
mean(merge(tweet_sentiments, mcdonaldsfull, by = "id", all = FALSE)$sentiment_score)
```
```{r}
mean(merge(tweet_sentiments, kfcfull, by = "id", all = FALSE)$sentiment_score)
```

```{r}
mean(merge(tweet_sentiments, subwayfull , by = "id", all = FALSE)$sentiment_score)
```
```{r}
mean(merge(tweet_sentiments, starbucksfull , by = "id", all = FALSE)$sentiment_score)
```

# Attributes:
# 4: Brand reputation
# 6: Advertising and Promotions
# 7: Food and Beverages
# 10: Social Media Engagement
```{r}
brand_sentiments = data.frame(matrix(nrow=4, ncol=4))
rownames(brand_sentiments) =  c("Mcdonalds", "KFC", "Subway", "Starbucks")
colnames(brand_sentiments) = c("Brand Reputation", "Advertising and Promotions", "Food and Beverages", "Social Media Engagement")
brand_sentiments$`Brand Reputation`= c(0.2195122, 0.9682647, 2.333333, 1.166667)
brand_sentiments$`Advertising and Promotions` = c(3.419355, -1.307692, 0.8888889, 2.380074)
brand_sentiments$`Food and Beverages` = c(0.8156028, 1.380952, 0.313253, 1.199275)
brand_sentiments$`Social Media Engagement` = c(1.015428, 1.622642, 1.52381, 2.061545)

x=cmdscale(dist(brand_sentiments, method = "euclidean", diag = TRUE, upper = TRUE), k=2)
plot(x[,1], x[,2], type = "n", main = "Perceptual Map of Fast-Food Brands", 
xlab="Advertising and Promotions", ylab = "Food and beverages" ,xlim=c(-3,3),ylim=c(-1.5,1.5))
text(x[,1], x[,2], row.names(brand_sentiments), cex = 1.2,col=c(3,4,6,8))
```
```{r}
brand_sentiments
x
```
```{r}
data.frame(x)
```

